Supermartingales and Termination Analysis of Statistical PCF

### 2021-04-29 LICS21/intro.tex
Fix references
It should not be possible to actually run bibtex without errors.

In this paper we study a central property of probabilistic programs: \emph{termination}.
When a probabilistic program implements a solution to an algorithmic problem, we naturally require the computation to terminate with probability $1$, in which case the program is called \emph{almost surely terminating} (AST).
Indeed, it is standard for designers and implementors of probabilistic programming systems to regard non-AST programs as defining invalid models, and hence inadmissible \cite{Rainforth2017,DBLP:conf/uai/GoodmanMRBT08}.
(Yet none of these systems provides any support for the development or verification of AST programs.)

>>>>

In this paper we study a central property of probabilistic programs: \emph{termination}.
When a probabilistic program implements a solution to an algorithmic problem, we naturally require the computation to terminate with probability $1$, in which case the program is called \emph{almost surely terminating} (AST).
Indeed, it is standard for designers and implementors of probabilistic programming systems to regard non-AST programs as defining invalid models, and hence inadmissible \cite{rainforth2017Automating,DBLP:conf/uai/GoodmanMRBT08}.
(Yet none of these systems provides any support for the development or verification of AST programs.)
